|

### 2021-04-27 05-Chp-CPRD-Analysis.Rmd
End of day: -2767

Originally termed the GPRD (General Practice Research Database),

@@

@@

@@

The analysis was adjusted for a range of baseline covariates including sex, grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010),

@@

All covariates were determined at index and definitions for each can be found in Supplementary Table 1.

@@

@@

Binary variables were modelled using a

continuo

As per best practice, all other variables, including the out

The MICE command in Stata was used

@@

In Cox models, there is the option to

Age vs time-since entry

Expand on use of age as the time scale, but describe the problems this introduced

@@

Hazard rations are

@@

<!--- This hasn't been done! --->

@@

@@

All code and summary statistics (i.e. the tables presented in this chapter, plus summary tables of effect estimates) are readily available in machine readable formats, without any formatting, from the Github repository for this project.

>>>>

Originally termed the General Practice Research Database,

@@

<!--- Insert flow-chart here --->

@@

Participants were followed up, and were censored at the earliest of date of diagnosis, death, date of transfer out of the study cohort or end of follow-up ( <!--- Get date here ---> )

_As a positive control outcome, we included cornonary artery disease. Statins have a known effect on this outcome on the basis of randomised controlled trials._

We also used a negative control of backpain to investigate the potential for residual confounding.

@@

The analysis was adjusted for a range of baseline covariates including sex,

grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010),

@@

All covariates were determined at index and definitions for each can be found in the archived data repository reflecting this study <!--- link to Zenodo here --->

@@

<!--- Review materials from multiple imputation course --->

@@

<!-- Binary variables were modelled using a -->

<!-- continuos -->

<!-- As per best practice, all other variables, including the out  -->

<!-- The MICE command in Stata was used -->

In the case of missing data, we used multiple imputation by chained equations (MICE) in STATA to create 20 imputed datasets. All covariates included in the analytic model were also included in the imputation model.

@@

<!-- In Cox models, there is the option to -->

<!-- Age vs time-since entry -->

<!-- Expand on use of age as the time scale, but describe the problems this introduced -->

To address the potential for immortal time bias, we employed a time-varying indicator of treatment status to correctly allocate time-at-risk to the exposed and unexposed groups.[@levesque2010] We ran two models, one unadjusted except for age, which was captured by using the participant's age as the time axis for the model,[@lamarca1998; @gail2009; @pencina2007] and a second adjusted for the additional covariates described above. Additional analyses stratified by outcome and drug class were also performed.

&nbsp;
<!----------------------------------------------------------------------------->

@@

Hazard ratios are

@@

<!--- This hasn't been done! Plus I do not think this is the case --->

@@

## Results

&nbsp;
<!----------------------------------------------------------------------------->

### Patient characteristics

&nbsp;
<!----------------------------------------------------------------------------->

### Primary analysis

### Sensitivity analyses

By pregnancy

By age-at-entry

By statin type (lipo vs hydrophilic)

### Controls

Backpain

Coronary artery disease

@@

All code and summary statistics (i.e. the tables presented in this chapter, plus summary tables of effect estimates) are readily available in machine readable formats, without any formatting (i.e. as comma separated values, or CSV, files) from the Github repository for this project. <!--- Will need to cite this, and may need to archive on Zenodo. --->
